\huge Open, privacy-preserving protocols for lawful surveillance

### 2016-02-29 paper/intersection.tex
s/dumps/records/

As described in Section~\ref{sec-introduction} and in~\cite{sff-foci2014}, the FBI used
set intersection to search for phone numbers that appeared in three sets of
cell-tower dumps. This procedure did not follow the the openness principle.
The FBI did not distinguish between targeted and untargeted users when
collecting the data. It only arrested the user in the intersection of the sets
it collected, as far as we know, but as there was no established accountability
procedure, we do not know whether the FBI retained the phone numbers of
untargeted users collected during the search, whether it subjected any of those
other phone numbers to additional investigation, whether it shared the data sets
of 150,000 total users with other government agencies, \emph{etc}.

>>>>

As described in Section~\ref{sec-introduction} and in~\cite{sff-foci2014}, the FBI used
set intersection to search for phone numbers that appeared in three sets of
cell-tower records. This procedure did not follow the the openness principle.
The FBI did not distinguish between targeted and untargeted users when
collecting the data. It only arrested the user in the intersection of the sets
it collected, as far as we know, but as there was no established accountability
procedure, we do not know whether the FBI retained the phone numbers of
untargeted users collected during the search, whether it subjected any of those
other phone numbers to additional investigation, whether it shared the data sets
of 150,000 total users with other government agencies, \emph{etc}.
